%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Safe font stack (ALWAYS AVAILABLE)
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{textcomp}

% Colors
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{10pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section Formatting
\titleformat{\section}{
  \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% Custom Commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2} \\
      \textit{#3} & {\color{dark-grey}\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey} #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Harshibar} \\ \vspace{5pt}
    \small
    Phone: \texttt{555.555.5555} \hspace{6pt} | \hspace{6pt}
    Email: \href{mailto:hello@email.com}{\texttt{hello@email.com}} \hspace{6pt} | \hspace{6pt}
    YouTube: \href{https://youtube.com/@harshibar}{\texttt{@harshibar}} \hspace{6pt} | \hspace{6pt}
    Location: U.S. Citizen
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{YouTube}{Aug. 2019 -- Present}
{Creator}{San Francisco, CA}
\resumeItemListStart
\resumeItem{Grew channel to \textbf{60k subscribers} in 1.5 years; created 80+ videos on tech and productivity}
\resumeItem{Conducted A/B testing on titles and thumbnails; increased video impressions by \textbf{2.5M} in 3 months}
\resumeItem{Designed a Notion workflow to streamline production; boosted productivity by 20\%}
\resumeItem{Partnered with brands like Skillshare and Squarespace for sponsorship collaborations}
\resumeItemListEnd

\resumeSubheading
{Google Verily}{Aug. 2018 -- Sept. 2019}
{Software Engineer}{San Francisco, CA}
\resumeItemListStart
\resumeItem{Led front-end development of a dashboard processing 50k blood samples for early cancer detection}
\resumeItem{Rebuilt a Quality Control product with 20 cross-functional stakeholders, saving \$1M annually}
\resumeItem{Spearheaded development of a new lab workflow tool, increasing efficiency by 40\%; shadowed core users and implemented solution end-to-end}
\resumeItemListEnd

\resumeSubheading
{Amazon}{May 2017 -- Aug. 2017}
{Software Engineering Intern}{Seattle, WA}
\resumeItemListStart
\resumeItem{Worked on Search Customer Experience Team; received a full-time return offer}
\resumeItem{Shipped a new feature to 2M+ users improving search for movie series queries}
\resumeItem{Built backend service in Java and implemented frontend UI}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Hyku Consulting}}{Sept. 2019 -- Mar. 2021}
\resumeItemListStart
\resumeItem{Mentored 15 students toward acceptance at top US boarding schools; achieved 100\% success rate}
\resumeItem{Designed collaborative ecosystem using Trello, Miro, and Google Suite}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Minimal Icon Pack}}{Sept. 2020 -- Nov. 2020}
\resumeItemListStart
\resumeItem{Designed and released 100+ minimal iOS and Android icons using Procreate and Figma}
\resumeItem{Generated \$250+ in sales through YouTube marketing and Gumroad distribution}
\resumeItemListEnd

\resumeProjectHeading{\textbf{CommonIntern}}{Sept. 2019 -- May 2020}
\resumeItemListStart
\resumeItem{Built Python automation tool using BeautifulSoup and Selenium for job applications}
\resumeItem{Achieved 500 GitHub stars; featured on Hackaday and Reddit communities}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart

\resumeSubheading
{Wellesley College}{Aug. 2014 -- May 2018}
{Bachelor of Arts in Computer Science and Pre-Med}{Wellesley, MA}
\resumeItemListStart
\resumeItem{\textbf{Coursework}: Data Structures, Algorithms, Databases, Computer Systems, Machine Learning}
\resumeItem{\textbf{Research}: MIT Graybiel Lab (published author), MIT Media Lab (urban microbe analysis)}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{SKILLS}
\begin{itemize}[leftmargin=0in,label={}]
\small{
\item{
\textbf{Languages}: Python, JavaScript (React.js), HTML/CSS, SQL \\
\textbf{Tools}: Figma, Notion, Jira, Trello, Miro, Google Analytics, GitHub, DaVinci Resolve, OBS
}}
\end{itemize}

\end{document}